SOURCE SEPARATION METHODS FOR COMPUTER-ASSISTED ORCHESTRATION

### 2021-06-08 source_separation/paper/paper.tex
Add and comment out cosine similarity equation
Reduce size of figures

  Source separation is an important addition to improve orchestration as it allows for the orchestration of more complex sounds in a way that makes sense in an orchestral context. Orchestral music often uses multiple layers, so by separating the layers of a target and individually orchestrating them, the resulting orchestration may improve.

@@

  \begin{figure*}[t]
    \centering
      \includegraphics[width=\textwidth]{figures/diagram.png}
      \caption{Diagram comparing the process of orchestration with and without separation. At the top, the full target orchestration is created simply by orchestrating the target. At the bottom, the separation process is performed, and the resulting sub-targets are individually orchestrated with subsets of the orchestra before being recombined to obtain the full orchestration.}\label{fig:full_diagram}
  \end{figure*}

@@

    \begin{figure*}[t]
      \centering
        \includegraphics[width=\textwidth]{figures/evaluation_diagram.png}
        \caption{Diagram showing the testing process. Note that in both orchestrations that use a split orchestra, they use the same division of the orchestra to orchestrate their four sub-targets.}\label{fig:eval_diagram}
    \end{figure*}

@@

    \begin{figure}[t]
    \centering
      \includegraphics[width=\columnwidth]{figures/orch.jpg}
      \caption{Example waveforms showing onsets of the four sources in the target, and possible onsets in the full, separated, and ground truth orchestrations. In this example, the separation method could not distinguish between sources 2 and 3 and identified them as a single sub-target. Therefore, the separated orchestration has only 3 onsets, one of them being an orchestration that combines sources 2 and 3. Note that this is a simplified representation, in the actual targets sources overlap in time and are not as discrete as this diagram shows.}\label{fig:orchestrations}
    \end{figure}

@@

@@

    Another aspect we would like to work on is the assignment of the orchestras. Currently, the subset of the orchestra that is assigned to each sub-target is randomly selected. However, it is possible that this random assignment could reduce the quality of the final orchestration. If, for example, one of the sub-targets contains mostly low pitch content, but the orchestra assigned to it contains mostly violins, violas, flutes, and oboes, the resulting orchestration will suffer. To solve this problem, a step could be added that jointly-optimizes the orchestras assigned to each sub-target, ultimately choosing an assignment that leads to the best orchestration of each sub-target.

>>>>

%  Source separation is an important addition to improve orchestration as it allows for the orchestration of more complex sounds in a way that makes sense in an orchestral context. Orchestral music often uses multiple layers, so by separating the layers of a target and individually orchestrating them, the resulting orchestration may improve.

@@

  \begin{figure}[t]
    \centering
      \includegraphics[width=\columnwidth]{figures/diagram.png}
      \caption{Diagram comparing the process of orchestration with and without separation. At the top, the full target orchestration is created simply by orchestrating the target. At the bottom, the separation process is performed, and the resulting sub-targets are individually orchestrated with subsets of the orchestra before being recombined to obtain the full orchestration.}\label{fig:full_diagram}
  \end{figure}

@@

    \begin{figure}[t]
      \centering
        \includegraphics[width=\columnwidth]{figures/evaluation_diagram.png}
        \caption{Diagram showing the testing process. Note that in both orchestrations that use a split orchestra, they use the same division of the orchestra to orchestrate their four sub-targets.}\label{fig:eval_diagram}
    \end{figure}

@@

    \begin{figure}[t]
    \centering
      \includegraphics[width=0.7\columnwidth]{figures/orch.jpg}
      \caption{Example waveforms showing onsets of the four sources in the target, and possible onsets in the full, separated, and ground truth orchestrations. In this example, the separation method could not distinguish between sources 2 and 3 and identified them as a single sub-target. Therefore, the separated orchestration has only 3 onsets, one of them being an orchestration that combines sources 2 and 3. Note that this is a simplified representation, in the actual targets sources overlap in time and are not as discrete as this diagram shows.}\label{fig:orchestrations}
    \end{figure}

@@

%Equation explanation needed
%Equation citation needed
%
%\begin{equation}
%	M(P(t),P(c)) = 1 - \left( \frac{\langle P(t), P(c) \rangle}{\|P(t)\| \cdot \|P(c)\|} \right)
%\end{equation}

@@

%    Another aspect we would like to work on is the assignment of the orchestras. Currently, the subset of the orchestra that is assigned to each sub-target is randomly selected. However, it is possible that this random assignment could reduce the quality of the final orchestration. If, for example, one of the sub-targets contains mostly low pitch content, but the orchestra assigned to it contains mostly violins, violas, flutes, and oboes, the resulting orchestration will suffer. To solve this problem, a step could be added that jointly-optimizes the orchestras assigned to each sub-target, ultimately choosing an assignment that leads to the best orchestration of each sub-target.
